% Chapter Template

\chapter{Research Objective} % Main chapter title

\label{Chapter3} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

Classification of research program(national program, local government program, industrial program, university program, self-selected topic or others):

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Anticipated Contribution}

Global vs local planning.
-> Local planning with advantages of optimization of global strategies.

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Subsection 1}

Nunc posuere quam at lectus tristique eu ultrices augue venenatis. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Aliquam erat volutpat. Vivamus sodales tortor eget quam adipiscing in vulputate ante ullamcorper. Sed eros ante, lacinia et sollicitudin et, aliquam sit amet augue. In hac habitasse platea dictumst.

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Subsection 2}
Morbi rutrum odio eget arcu adipiscing sodales. Aenean et purus a est pulvinar pellentesque. Cras in elit neque, quis varius elit. Phasellus fringilla, nibh eu tempus venenatis, dolor elit posuere quam, quis adipiscing urna leo nec orci. Sed nec nulla auctor odio aliquet consequat. Ut nec nulla in ante ullamcorper aliquam at sed dolor. Phasellus fermentum magna in augue gravida cursus. Cras sed pretium lorem. Pellentesque eget ornare odio. Proin accumsan, massa viverra cursus pharetra, ipsum nisi lobortis velit, a malesuada dolor lorem eu neque.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Research Plan}

The research plan is devided into
three main categories which are the framework for experiments in simulation,
the framework for experiments in real world and
the perception and planning algorithm.

\subsection{Framework for Experiments in Simulation}

\begin{itemize}
    \item Build race track.
    \item Compute global trajectory.
    \item Track global trajectory.
    \item Implement data link (onboard camera)
    \item Implement automized training of neural network.
    \item Implement test scenarios.
\end{itemize}


\subsection{Framework for Experiments in Real World}

\begin{itemize}
    \item Find location and build race track.
    \item Deploy localization algorithm.
    \item Run hardware.
    \item Safety regulations.
    \item Finance.
    \item Compute global trajectory.
    \item Track global trajectory.
    \item Implement data link (onboard camera)
    \item Implement automized training of neural network.
    \item Implement test scenarios.
\end{itemize}
    

\subsection{Perception and Planning Algorithm}

\begin{itemize}
    \item Develope algorithm
    \item Design neural network
    \item Implement algorithm
    \item Optimize efficiency for onboard execution
\end{itemize}

Scheduled time of completion of reading and investigation: 
Scheduled time of completion of research work:
Equipment for experiment and other research facilities

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Methodology and Elaboration}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.

%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Solutions}

Sed ullamcorper quam eu nisl interdum at interdum enim egestas. Aliquam placerat justo sed lectus lobortis ut porta nisl porttitor. Vestibulum mi dolor, lacinia molestie gravida at, tempus vitae ligula. Donec eget quam sapien, in viverra eros. Donec pellentesque justo a massa fringilla non vestibulum metus vestibulum. Vestibulum in orci quis felis tempor lacinia. Vivamus ornare ultrices facilisis. Ut hendrerit volutpat vulputate. Morbi condimentum venenatis augue, id porta ipsum vulputate in. Curabitur luctus tempus justo. Vestibulum risus lectus, adipiscing nec condimentum quis, condimentum nec nisl. Aliquam dictum sagittis velit sed iaculis. Morbi tristique augue sit amet nulla pulvinar id facilisis ligula mollis. Nam elit libero, tincidunt ut aliquam at, molestie in quam. Aenean rhoncus vehicula hendrerit.


%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------

\section{Schedule of Thesis Writing and Proposed Date of Defense}

I intend to complete the research,
which includes programming solutions
as well as conducting tests in simulation and real world,
until the mid of December 2019,
when I am going to return to Germany.
If points of the research plan will not have been complied by then,
I am going to finalize them at 
the Technical University of Berlin
starting from New Year on.
Directly after, I am going to start writing my master thesis.
At my present discretion,
I will finalize the thesis until
the end of February 2020.

According to the regulations of the
Double degree master of -------------------
I am going to achieve remaining credits in September,
by the end of the spring semester 2020.
Subsequently, having all requirements of the program fulfilled,
I am going to do my final defense in October 2020
either by appearance in person or video conference.


Outline of the thesis and schedule of thesis writing:

