%----------------------------------------------------------------------------------------
%	CHAPTER 2 - LITERATURE REVIEW
%----------------------------------------------------------------------------------------
%========================================================================================

\chapter{Literature Review} \label{Chapter2}

For the last few years
numerous, newly developed
UAV technologies have been
successfully applied in 
industry and
projects of public interest.
Meanwhile, 
major companies and
research centers across the globe
are researching on further UAV based solutions.
Employing the benefits of machine learning, 
new approaches for autonomous navigation
that outperform traditional approaches 
have been published.
Still, the robustness
of autonomous systems 
is not sufficient to
safely deploy them in many, desired
areas of application. 
Increasing the level of autonomy and
improving robustness,
e.g. enable UAVs to safely operate in 
dynamic environments like urban areas,
is thus, most significant
for further 
integration of
UAV technologies
into public life.

This chapter ...


%----------------------------------------------------------------------------------------
%	SECTION 1 - CLASSIFICATION OF UNMANNED AERIAL VEHICLE
%----------------------------------------------------------------------------------------

\section{Classification of Unmanned Aerial Vehicles} \label{Chapter2Section1}

\textit{This section provides a definition 
for the term of an unmanned aerial vehicle (UAV)
and introduces common classification approaches
in order to subsequently integrate the
quadcopter MAV 
which I am going to deploy 
within the research of my master thesis.}

An unmanned aerial vehicle (UAV),
often referred to as drone, is an
aircraft without a human pilot onboard.
Core components of an UAV are an airframe,
an autopilot, onboard sensors and 
data link. 
While the airframe constitutes the mechanical structure,
the autopilot is the fundamental control unit of an UAV.
It translates higher control commands,
e.g., to track a trajectory,
into individual motor commands
and autonomously performs basic navigation tasks,
e.g., to stabilize the aircraft or to maintain the pose,
as support to a human pilot or as part of a preprogrammed mission
or of an fully autonomous control structure.
Onboard sensors such as
an inertial measurement unit (IMU), 
a satellite-based navigation sensor,
a video camera
or a light detection and ranging (LIDAR) sensor, 
supply the autopilot and optionally
existing, superior control units,
with the necessary data input.
Data link enables the UAV to
exchange digital information.
Optional components of an UAV,
e.g., a companion computer
for increased computational power,
can be mounted onboard.
One or more UAVs,
combined with one or more
ground control stations (GCS),
form an unmanned aerial system (UAS).
At the GCS, data from the UAV
is processed and the UAV 
is either steered by human pilot or
instructed to fly a preprogrammed mission or autonomously.
While the quadcopter is the best-known representative,
various different types of UAVs exist
which are classified by means of
different criteria, 
i.e., airframe type and key characteristics.
\cite{Fahlstrom2012}
However, a universal, international classifying system
does not exist.

%----------------------------------------------------------------------------------------
% subsection 1 - Classification by Airframe Type

\subsection{Classification by Airframe Type} \label{Chapter2Section1Sub1}

Airframe type and 
the particular configuration
of an UAV
have big impact on its
capabilities to navigate in
various applications 
and environments.
\cite{Kong2010}
Austin introduces three main categories
of airframe types, i.e.
horizontal take-off and landing (HTOL),
vertical take-off and landing (VTOL)
and hybrids.
\cite{Austin2011}
\textbf{HTOLs}
are foremost represented by airplanes
which are composed of fixed wings
and a propulsion unit.
When moving forward, the wings
generate lift that compensates gravitational force
by accelerating horizontally incoming
air downwards.
The wings also have stabilizing effects
on the aircraft and hold
control surfaces that
enable navigation.
HTOL is
the most aerodynamically efficient airframe configuration
and therefore, suitable for missions
with high speed as well as
long flight range and time.
Since lift generation depends on forward motion,
a HTOL cannot maintain position and
its launching and landing 
require infrastructure, either a runway or
a launch and recovery system.
Thus, HTOLs cannot be deployed
on missions which entail
hovering or lack
launching and landing infrastructure,
e.g., business-to-customer (B2C) delivery in densely populated areas.
\textbf{VTOLs}
are foremost represented by
copters wich are composed of a single or multiple rotors.
A copter generates lift by rotating its rotor(s)
and accelerating air downwards.
Since the air is drawn in from above the rotor(s),
a copter is able to hover as well as launch and land vertically.
Besides vertical force,
a running rotor induces also torque
on the aircraft.
In case of a helicopter (single rotor copter),
an additional, small tail rotor
cancels the torque of the main rotor and 
stabilizes the yaw of the aircraft.
In case of a multicopter,
the torques counter themselves
due to the fact that individual rotors
are arranged in opposite directions of rotation.
Depending on particular aircraft design, 
navigation is achieved by
adjusting either rotational speed 
or tilt of constituent rotors
in order to
generate differential thrusts and torques.
At the prize of lower flight speed, range and time,
VTOLs are suitable in situations which
require hovering as well as launching and landing on small areas 
without previously installed infrastructure.
\textbf{Hybrid Systems}
combine benefits of HTOLs and VTOLs,
i.e., the ability of vertical take off and landing
as well as the speed necessary for 
long range and high altitude flights.
This is usally realized by
either 90 degree tilting rotors or
an array of 90 degree tilting jets mounted on 
the fixed wings and fuselage of a HTOL.

%----------------------------------------------------------------------------------------
% subsection 2 - Classification by Key Characteristics

\subsection{Classification by Key Characteristics} \label{Chapter2Section1Sub2}

Official authorities 
published various classification systems for UAVs
with respect to technical specifications
and key characteristics.
Most of the classification
systems come from 
the military sector,
e.g., the five UAS groups based on
maximum gross takeoff weight, normal operating altitude
and airspeed published by the United States Department of Defense
\cite{USDOD2011}.
But there also exists
classification for the civil realm,
e.g., 
the seven classes based on empty weight, take-off weight
and usage published by the Civil Aviation Administration of China
\cite{Wei2016}. 
Watts, Ambrosia and Hinkley\cite{Watts2012} propose a classification
for civil, scientific usage.
Mentionable UAV classes of their
classification are
micro air vehicles (MAV),
low altitude, short endurance (LASE),
low altitude, long endurance (LALE),
medium altitude, long endurance (MALE)
and high altitude, long endurance (HALE).
For their key characteristics,
see table \ref{tab:CivilRealmClassificationUAV}.

\begin{table}
    \caption{Classification of UAVs in the civil realm by Watts, Ambrosia and Hinkley. \cite{Watts2012}}
    \label{tab:CivilRealmClassificationUAV}
    \centering
    \begin{tabular}{r l l l l}
    \toprule
    \tabhead{Class} & \tabhead{Altitude} & \tabhead{Endurance} & \tabhead{Range} & \tabhead{Takeoff / Landing} \\
    \midrule
    MAV     & < 330 m       & < 30 min  & < 1 km        & Any small area \\
    LASE    & < 450 m       & < 2 h     & < 10 km       & Human hand, catapult system or runway \\
    LALE    & < 5,000 m     & < 20 h    & < 100 km      & Runway \\
    MALE    & < 9,000 m     & < 40 h    & < 1,000 km    & Runway \\
    HALE    & < 25,000 m    & < 30 h    & < 10,000 km   & Runway \\
    \bottomrule\\
    \end{tabular}
\end{table}

%----------------------------------------------------------------------------------------
% subsection 3 - The UAV of my research

\subsection{The UAV of my Research} \label{Chapter2Section1Sub3}


For the research within my master thesis,
I have two quadcopter MAVs at hand
which differ only in the fact that
one of them has an additional companion
computer.

FOTO


%Multicopters, in turn, are classified by the number
%of rotors and their arrangement, e.g. a "quadcopter +" has four rotors
%arranged along a symmetric plus sign.
%https://s3.amazonaws.com/academia.edu.documents/32160055/Unmanned_Air_Systems_UAV_Design__Development_and_Deployment.pdf?response-content-disposition=inline%3B%20filename%3Dfor_UAV_design_and_operation.pdf&X-Amz-Algorithm=AWS4-HMAC-SHA256&X-Amz-Credential=AKIAIWOWYYGZ2Y53UL3A%2F20190910%2Fus-east-1%2Fs3%2Faws4_request&X-Amz-Date=20190910T014051Z&X-Amz-Expires=3600&X-Amz-SignedHeaders=host&X-Amz-Signature=21449b6e7e8260c2e71e5593e49acfda353cbc2e66d60e046c0469be451f14f4

The quadcopter configuration is the most common
airframe for UAVs in the civil realm. 
For all multicopters,
electronic complexity in form of multiple motors,
speed controllers and a power distribution board
as well as an autopilot,
which computes individual motor speeds in order to
stabilize the aircraft and follow navigation inputs,
replace the mechanical complexity of
helicopters. 
However, due to extensive cost decrease
and performance increases from the year of 2000 on,
huge markets and broad research on UAVs, exspecially multicopters,
have been established.
%https://dspace.mit.edu/bitstream/handle/1721.1/121319/Garcia_Santoso_2019.pdf?sequence=1&isAllowed=y



However, the insights of my master thesis
will be reproducible for other configurations
of multicopters because my research
takes place on a higher level of navigation control.
and low level control of individual motors is excluded.
Thus, common autopilots can
cancel the differences between the various
configurations of multicopters and can ensure
an essentially similar flight behaviour.








%----------------------------------------------------------------------------------------
%	SECTION 2 - COMMERCIAL AND CIVIL APPLICATIONS OF MULTICOPTERS
%----------------------------------------------------------------------------------------

\section{Commercial and Civil Applications of Multicopter UAVs} \label{Chapter2Section2}

UAV technology has its historic origin
in military affairs from the 1930's.
They had been mostly confined to military use.
During the transition to the new millennium,
electronic components were rapidly improving performance
and, at the same time, essentially decreasing acquisition costs.
Thus, UAV technologies have been becoming 
accessible for the wider public.
A huge consumer UAV market for private customers
has been established 
with the quadcopter MAV as the public's first association to UAVs.
Many UAV manufacturing
companies
(above all, the China based UAV manufacturer DJI,
which in 2014 accounted for a global market share of consumer UAV sales of
approximately 70 percent
\cite{Statista2015})
have been founded and
operate successfully in the worldwide business
of consumer UAVs.
Numerous innovative
UAV designs, concepts and algorithms
developed within these companies, open source projects and public research,
opened the door for UAV technologies
to commercial applications in industry
and civil projects of public interest
around
the year of 2015.
Right now, the commercial and the civil applications of UAVs
are evolving rapidly to a prognosticated market size of
13 billion U.S. dollars from 2016 to 2020 \cite{Goldman}.
UAVs are exspecially useful on missions
which are either characterized 
as dangerous or as inefficient, 
i.e., "human pilot operations would be at a disadvantage or at high risk" \cite{Watts2012}.
The ability to efficiently gather data from an overviewing perspective of a bird
is a great benefit considering terms such as big data, cloud computing and machine learning.
\cite{Garcia2019}

This section exemplarily introduces
fields of current and upcoming applications in order
to demonstrate the great, social and economic value
that UAV technology has already shown or will achieve in the future.
Moreover, limiting factors hindering
the breakthrough of UAVs into the public life
are discussed together with current research
to eliminate these factors.
Thereby, the focus is on the application field of
business-to-customer (B2C) delivery
which probably will be the most revolutionary, future UAV application
for the modern public life and
whose prosperous 
realization depends foremost, 
on the development of robust,
autonomous flight in dynamic environments -
a topic to which my master thesis shall contribute.


%----------------------------------------------------------------------------------------
% Potential subsections
%\subsection{Freight Traffic}
%\subsection{Power and Utilities Industry} %https://www.pwc.pl/en/drone-powered-solutions/Articles/Drone-Powered-Solutions-for-Power-Utilities-Sector-New-Report-by-PwC-DPS.html
%\subsection{Passenger Transport} %https://www.pwc.pl/en/drone-powered-solutions/Articles/self-flying-taxi-in-dubai.html
%\subsection{Cellular Connectivity} %https://www.pwc.pl/en/drone-powered-solutions/Articles/2018/drone-as-emergency-ad-hoc-networks.html




%----------------------------------------------------------------------------------------
% subsection x - Agriculture

\subsection{Agriculture}

Broader application of UAV technologies in agriculture 
is a partial solution to satisfy 
increasing agricultural consumption
in the light of, first, the predicted growth of world's population
over the next decades 
and, second, the increase of
extreme weather conditions due 
to the climate change. 

For the last few years,
farmers have been integrating UAVs into their work
to overcome the "largest obstacle" \cite{Ahirwar2019} in agriculture,
i.e., the inefficiency caused by the vastness of farmlands.
Due to the ability of UAVs to
navigate freely above the fields, 
various types of sensors (spectral, thermal, vision, etc.) 
are able to gather 
comprehensive data from the bird's eye view.
That enables the deploy of
powerful analysis methods in agriculture
which in turn, have the potential to
increase productivity
and to reduce costs as well as the use of chemicals
contaminating the ground water.
Various start-ups supply
UAV technologies
that together cover almost the whole crop lifecycle,
i.e., soil analysis as the basis of irrigation and nitrogen management as well as planting patterns \cite{DeveronUAS},
seed planting with individual nutrient supply \cite{DroneSeed}, 
crop spraying with the precise, necessary amount of chemicals \cite{HSE} and
crop monitoring for health and economic assessment,
determination of the harvest date as well as 
documentation for potential insurance cases \cite{PrecisionHawk}.
In this sense, JD.com,
which is the second biggest Chinese online retailer
and pioneer in UAV and smart technology,
launched the initiative,
\textbf{"JD Smart Agriculture Development Community"}
aiming at increased efficiency of the agriculture industry
and improved quality and safety of foods in China.
Thereby, the UAV technologies developed
by the researchers of JD-X, 
the logistics innovation lab belonging to the firm,
are deployed to protect crop
, i.e., to 
"monitor and analyze water, soil, pesticides, fertilizer, weather, diseases and pests"
\cite{JD.com2018}.

In contrast to dynamic, urban areas, the vastness of farmlands
present a structured, predominantly static environment
that allows state of the art UAV technology to be safely deployed.
Most significant for the breakthrough of UAVs in agriculture is thus,
further automation to increase efficiency
as well as 
the development of more powerful sensors to increase the 
quality of the gathered data.

\cite{Mazur2016}\cite{Ahirwar2019}


\subsection{Healthcare}

%https://onlinelibrary.wiley.com/doi/pdf/10.1111/trf.15195
%https://flyzipline.com/impact/
%http://en.people.cn/n3/2019/0410/c90000-9565324.html


\subsection{Environmental Protection}
%https://www.chinadaily.com.cn/a/201909/04/WS5d6f1680a310cf3e3556999d.html
%https://www.chinadaily.com.cn/a/201907/12/WS5d27dc46a3105895c2e7d0f6.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/surfers-enjoying-the-charms-of-australian-beaches-will-be-protected-from-sharks-by-drones.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/Drone-technologies-help-communities-in-Poland-deal-with-the-impact-of-storms.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/2018/drone-environment-inspections-in-china.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/Intelligent-drones-will-save-wildlife-in-Africa.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/how-qut-drones-will-save-koalas.html
%https://www.pwc.pl/en/drone-powered-solutions/Articles/drones-as-tornado-chasers1.html

\subsection{B2C Delivery Service} \cite{Watts2012}
%https://mydroneauthority.com/industry/drone-delivery/


\paragraph{Introduction}
tests are being conducted, 
what big companies and startups are doing, \
and where it is possible to see the technology in action.


For a few years the idea of 
delivery drones transporting parcels, food and other goods
directly to customers
has manifested in several pioeneer applications. 
Researchers are working hard on this hot topic
which will reduce delivery time,
costs.

\paragraph{Potential}
Drone delivery technologies have big potential
of improvements in various aspects.

From economic considerations,
drone delivery is a better solution to the "last mile problem"
which refers to the high costs occurring during the last, inefficient step of supply chains.
On short distances from a transportation hub to final destinations,
drones can be faster while consuming less fuel. Costs related
to traditional delivery on the "last mile" such as
<labor costs for human drivers> and <fleet maintenance of commercial vehicles>
are omitted.
https://www.statista.com/statistics/816884/last-mile-delivery-logistics-providers-challenges/

In the field of healthcare,
drones show promise to speed up emergency response
where the time from incident to first measure is 
most critical and 
congestion might be fatal.
Hastening the supply of emergency medicine,
donated blood and portable medical devices as well as
enabeling paramedics to instruct helpers on site from a far distance
is life saving in case of misfortunes like 
heart attacks, strokes and external injuries.

Because drones are electrically powered, they provide benefits
with respect to climate protection if batteries
are recharged with renewable resources. Moreover,
the operation of drones is emmision-free and thus,
an answer to the air pollution problems
which occurs in metropoles across the globe [QUELLEN Deutschland, China, Indien, USA].

<overcoming delivery problems to remote areas>


\paragraph{Applications}

The concept of commercial drone delivery started in 2013
when Amazon announced their initiative "Amazon Prime Air" of developing drone systems for 
parcel delivery.
%https://www.nytimes.com/2016/08/11/technology/think-amazons-drone-delivery-idea-is-a-gimmick-think-again.html
%https://www.amazon.com/b?node=8037720011
%https://www.youtube.com/watch?v=98BIu9dpwHU
%https://smallbiztrends.com/2013/12/amazon-drones-prime-air-delivery-30-minutes.html

Within less than a week, UPS reacted on the new competitor in its core business with
announcing their own plans of drone delivery.
%https://www.youtube.com/watch?v=xx9_6OyjJrQ
%https://smallbiztrends.com/2013/12/ups-delivery-drones.html 

Trapped by regulations

FAA rules currently prohibit drone flights 
that are entirely autonomous or 
beyond the line of sight of human operators. 
7-Eleven has managed to work within those regulations
by using its delivery service as a means to advance research 
toward integrating drones into the National Airspace System, 
while also helping further refine Flirtey’s delivery technology.



Nevertheless, in the shadow of these gigantic players,
in July 2015 Flirtey, an Australian start-up, performed the first
federally-approved commercial drone flight in the U.S.
%https://www.youtube.com/watch?v=xEm7bI_meQY
%https://smallbiztrends.com/2015/07/first-drone-delivery-flirtey.html
%https://www.flirtey.com/

Thereupon in July 2016, Flirtey in corporation with 
the convenience store chain 7-Eleven 
performed the first "store-to-door" drone deliveries to private customers
in the US with an autonomously flying drone relying on precision GPS.
%https://www.youtube.com/watch?v=7amSm_Yh7DY
%https://www.prnewswire.com/news-releases/flirtey-and-7-eleven-complete-first-month-of-routine-commercial-drone-deliveries-deliver-77-packages-to-customer-homes-in-united-states-300381798.html

In December 2016, Amazon caught up with its first drone delivery
in the UK. 
<drone flights that are entirely autonomous or beyond the line of sight of human operators,
The UK and several other countries have taken more pro-innovation regulatory positions
Amazon chose the country with a regulatory climate that is more conducive to proper UAV testing and subsequent application
>
%https://www.youtube.com/watch?v=vNySOrI2Ny8
%https://www.amazon.com/b?node=8037720011
%https://smallbiztrends.com/2016/12/faa-drone-regulations.html

In August 2017, the icelandic start-up Aha in corporation with Israeli logistics system Flytrex 
started a project to fly drones 
manufactured by the biggest Chinese drone company DJI
on preprogrammed missions to deliver consumer goods to customers' houses
in Rejkjavik the capital of Iceland. 
Iceland previously opened its regulations for this project.
\cite{Ross2018}


October 2016 Zipline


With its huge population (1.4 billion people in 2018)
eCommerce Report
and broad social acceptance towards digital innovations
-in comparison 39\% of US American citizens
are sceptical towards drone delivery
https://www.statista.com/chart/5843/level-of-trust-in-drone-delivery-services/-,
China surpassed the United States of America in 2013 and
became the biggest eCommerce market worldwide with
a total revenue of approximately 633.9 billion USD in 2018
leaving the US on second place with 501.0 billion USD and 
the European Union on third place with 358.1 billion USD.
eCommerce Report
https://www.techinasia.com/2013-china-surpasses-america-to-become-worlds-top-ecommerce-market
https://www.statista.com/study/42335/ecommerce-report/

The growth of eCommerce has
strong impact on the logistics market
demanding innovative and efficient approaches
for fast and reliable door step parcel delivery shipment
even in remote areas with little infrastructure.



 
logistic companies.
The China-based companies DJI, ... are among the biggest drone developers and producers
and came up with highly engineered, innovative drone systems.
For individuals as well as in corporation with the
dominating shipment companies JD, SF Express, in China.

Several China-based companies 
are testing drone delivery supported by
innovative drone comanies such as DJI.


https://www.scmp.com/tech/innovation/article/2129585/jdcoms-autonomous-delivery-vehicles-will-take-streets-tianjin-june
After the approval by the China Civil Aviation Administration
<build tens of thousands UAV landing platforms or drone pods across China>
JD.com extended its drone projects
with own UAV, unmanned ground vehicles, and unmanned warehouses
within its JDX Department for intelligent logistics.
https://technode.com/2018/02/05/e-commerce-giant-jd-will-build-tens-of-thousands-delivery-drone-landing-pods/
https://jdcorporateblog.com/jd-com-announces-series-of-new-agreements-for-drone-development/
https://jdcorporateblog.com/jd-com-to-build-largest-drone-logistics-network-and-rd-campus-in-china/


While the logistics subsidiary of JD.com
which is the second biggest business to customer (B2C) eCommerce company
in China after Tmall of the Alibaba Group
%https://www.statista.com/statistics/959881/china-gmv-share-of-online-retail-b2c-market-by-platform/
was opening its first UAV distribution center in Haikou, the capital of Hainan in 2018,
the first company that received a license for drone delivery services
by responsible Chinese administration was Jiangxi Fengyu Shuntu Technology Company.
%https://technode.com/2018/03/28/first-licence-for-drone-deliveries-in-china-goes-to-sf-express/
%http://www.xinhuanet.com/finance/2018-03/28/c_1122600619.htm
The company is an affiliated company of SF Express 
which is one of the biggest delivery service companies in China 
%https://www.statista.com/statistics/244034/leading-logistics-companies-in-china-by-revenue/
An airborne supply chain consisting of nationwidely operating planes,
locally distributing larger drones and customer delivering smaller drones
should foremost increase the coverage of delivery and
the delivery time in rural areas.
%https://technode.com/2018/03/28/first-licence-for-drone-deliveries-in-china-goes-to-sf-express/

<
Its first drone took off on 26 March on its way to the company’s first Hainan delivery (in Chinese). Hainan is an island off the southern coast of the mainland and is highly mountainous and so a suitable testing ground for the format. JD has ambitions to be able to deliver anywhere in the country within 24 hours.>
%http://tech.sina.com.cn/i/2018-03-26/doc-ifysqfnh0749009.shtml
%https://jdcorporateblog.com/jd-com-launches-new-institute-for-smart-logistics-in-urban-areas-2/



International
Corporation with Rakuten in Japan
%https://jdcorporateblog.com/jd-com-and-rakuten-to-collaborate-on-unmanned-delivery-solutions-in-japan/
Indonesia
%https://jdcorporateblog.com/gallery/jd-com-launches-first-government-approved-drone-flight-in-indonesia-2/




JD.com
Alibaba
<This Chinese company is pursuing a massive and rapid expansion of a commercial drone delivery system in the four most-populated provinces in China. The drones fly from centralized warehouses to locally-designated landing pads. More than 300,000 local delivery operators then take the packages to the nearby homes. This company has small commercial drones that can fly up to 62 mph (100 kph) and carry up to 66 lbs. (30 kg). It also has a very large commercial drone that can carry up to one metric ton (2,200 lbs.). >
DHL
In December of 2013, DHL started delivering medicines using drones in Germany. 

Alibaba 
In February 2015, Alibaba partnered with the courier company Shanghai YTO Express to deliver tea by commercial drones to 450 customers in certain Chinese cities. 

Alphabet (Google) 

Google has many ongoing drone programs and tests underway including Alphabet X, which partnered with Chipotle Mexican Grill to deliver food to the cafeterias on the Virginia Tech Campus. Since 2014, Alphabet X has been testing drone delivery service ins Australia to deliver both consumer items and much heavier things such as building materials. Project Wing delivers medicines and burritos in rural areas. 





\paragraph{Limiting factors}
The breakthrough of drone delivery
has not been taken place yet due to several
limiting factors.

In contrast to the previously mentioned
environment-friendly abilities,
current, typical drone models emit a buzzing noize.
Thus, an extensive application of drone delivery,
would lead to new, dominant source of noise pollution 
which affects the quality of life in urban areas.



Safety Concerns - include damage and injury caused by 
accidents, 
flyaways, 
privacy issues, 
security, and 
package interference from stealing or vandalism. 

Due to little experience of drones
participating in daily traffic,
consequences of traffic accidents caused
by drones are difficult to predict. 
There have not been recorded any fatal commercial drone crash until now
%(https://www.researchgate.net/publication/291697791_A_Technocritical_Review_of_Drones_Crash_Risk_Probabilistic_Consequences_and_its_Societal_Acceptance),
???and the risk of autonomous flight is estimated very low ?????
%(https://www.researchgate.net/publication/27467796_A_Casualty_Risk_Analysis_For_Unmanned_Aerial_System_UAS_Operations_Over_Inhabited_Areas) 
but a lot of near-accidents and injuries are reported
%(https://www.techrepublic.com/article/12-drone-disasters-that-show-why-the-faa-hates-drones/)
%https://eu.usatoday.com/story/news/nation/2014/09/03/charges-brought-in-drone-crashes/15041623/
%https://www.cnet.com/news/this-hawk-has-no-love-for-your-drone/
%https://www.pcmag.com/news/351016/video-drone-crashes-into-seattles-space-needle
%https://medium.com/@obox/the-world-thinks-i-faked-a-drone-crashing-into-my-office-window-and-head-10a732d62e74
%https://www.cbsnews.com/news/decision-announced-on-charges-in-white-house-drone-incident/
.
Not least because of the uncontrolled nature of drone crashes,
the deploy of drone technologies in daily life is seen critically by
local administrations and
is legally restricted by local laws of the states.
??autonomous and human pilot.??
To give a few examples, 
in the United States of America, 
law forbids the navigation of drones above other persons Quelle!!!(December 2018) 
In cities, drone delivery would be only legally possible on air corridors for drones
and would lose its advantage of not being bound to existing infrastructure
and thus, could be affected by congestion and circuitous routes.
Moreover, according to the Federal Aviation Administration (FAA) in the United States,
out-of-sight drone navigation with a virtual reality headset needs a special permission
which further limits drone delivery in not fully visible delivery areas like cities.
autonomous???

Privacy is another concern when it comes to drone navigation
and led to legal restriction.
Drone systems are equipped with different sensors,
visual, range, can look through walls etc.
and would enter spheres which until now have not been
reached by them. A single drone can look through windows at high levels
or see what happens behind a tall fence. A whole fleet of
delivery drones can profile entire societies if their data
is combined and evaluated with methods of artificial intelligence.
%https://www.pwc.pl/en/drone-powered-solutions/Articles/Can-drones-see-through-walls.html

By law, unauthorizedly overflying restricted areas of critical infrastructure 
such as nuclear power plants
%https://www.researchgate.net/publication/291697791_A_Technocritical_Review_of_Drones_Crash_Risk_Probabilistic_Consequences_and_its_Societal_Acceptance
and military bases is forbidden.
Losing control of drones in case of navigation failure or hacker attack
can be punished by heavy fines or even imprisonment.

Another concern is the security of delivered items
which decisively affects the consumers to accept this new way of delivery.
%https://www.emarketer.com/Article/How-Do-Consumers-Feel-About-Drones-Delivering-Their-Packages/1014138
Finding convenient solutions to criminal actions such as the downing of drones 
or the stealth of delivered parcels as well as 
technical questions, e.g. protection of the parcel against rain and outer forces
as well as a robust approach of handing it over, are crucial here.


<Realistically, however, implementation could take three to five years, and that’s just to get FAA approval. There may be other problems, too, in densely populated cities like Washington D.C. where no-fly zones are currently in place.

Brendan Schulman, special counsel at Kramer Levin Naftalis and Frankel LLP told the Associated Press:

    The technology has moved forward faster than the law has kept pace.>
%https://smallbiztrends.com/2013/12/amazon-drones-prime-air-delivery-30-minutes.html


\paragraph{Current Research}
Current research on Future Solutions

%http://en.people.cn/n3/2019/0818/c98649-9606973.html

noise pollution problem, 
Edgar Herrera, developed a blade-less drone. 
It flies in complete silence. 
The drone is not yet in production; 
however, the design is spectacular. 
Solar-powered, silent-flying, drone delivery is a really great idea that takes this whole concept to the next level.
In the future, there may be overly-active, 
drone-flying corridors that are constantly buzzing. 
%https://www.google.com/search?client=ubuntu&channel=fs&q=bladless+drone+no+noize&ie=utf-8&oe=utf-8


Legal restrictions with more robust technology.
<Using drones equipped with emergency parachutes, 
which automatically deploy for power losses, 
can help reduce crash damage and injuries. 
There are plenty of opportunities for entrepreneurs to improve drone-flying safety. >


<Drones equipped with video surveillance technology can reduce these criminal risks; however, these cameras cause privacy and security issues to arise. This is an area of opportunity, where entrepreneurs can focus on providing solutions. >

-----


already capable of being deployed for many types of delivery services 
such as pizzas in urban environments and 
desperately-needed medicine flown by drones to remote inaccessible villages.
%https://spectrum.ieee.org/robotics/drones/in-the-air-with-ziplines-medical-delivery-drones


already plenty of opportunities 
flying unmanned aerial vehicles (UAVs) for fun 
and for professional uses. %https://mydroneauthority.com/reviews/best-professional-drones/


%https://europe.chinadaily.com.cn/a/201905/16/WS5cdd33e3a3104842260bc192.html



%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Drone Racing}

%http://www.chinadaily.com.cn/m/jiangsu/wuxi/2019-08/28/content_37506351.htm


%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Civil Engineering}

%https://www.pwc.pl/en/drone-powered-solutions/Articles/drones-inspections-over-hard-to-reach-infrastructure.html


<rescue,   exploration,  environment  monitoring,  map  construction  or  search>
%https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8494201





















%----------------------------------------------------------------------------------------
%	SECTION 3 - THE FLIGHT CONTROL PIPELINE OF AN UAV
%----------------------------------------------------------------------------------------

\section{Navigation of an Autonomous Quadcopter}

HERE

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Low-level control by Autopilot}

HERE

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------
\subsection{High-level control}

<
They can be controlled by onboard electronic equipments 
or via control equipment from the ground. 
When it is remotely controlled from ground 
it is called RPV (Remotely Piloted Vehicle) 
and requires reliable wireless communication for control. 
Dedicated control systems may be devoted to large UAVs, 
and can be mounted aboard vehicles or in trailers 
to enable close proximity to UAVs that are 
limited by range or communication capabilities.
>


\paragraph{Human Pilot}
<When it is remotely controlled from ground 
it is called RPV (Remotely Piloted Vehicle) 
and requires reliable wireless communication for control.>







%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Autonomous Navigation Systems of Small Quadcopter UAVs}

For legal classification and restriction,
the International Civil Aviation Organization (ICAO)
devides UAVs into either fully remotely controlled 
or fully autonomous.
%https://www.icao.int/Meetings/UAS/Documents/Circular%20328_en.pdf
From technical perspective,
autonomy is not a static
but a fluent feature of an UAV
and thus, more precisely referred to as
degree of autonomy. For example,
even a remotely piloted vehicle (RPV)
usually involves an autopilot
which supports the human pilot
during flight by autonomously
performing tasks, e.g. maintaining pose.
%and translation of higher order navigation tasks
%to individual lower level motor commands.
This section recaps a general
concept of autonomy as well as
a hierarchical control architecture for a
fully autonomous UAV in order to
subsequently introduce
autonomous navigation systems of UAVs.
Traditional and newly developed methods
related to autonomous navigation
as well as 
the research of this work are classified.





\subsection{Dynamics and Control}

During flight, an UAV is an unstable system
and requires continual control.
Traditionally, this control is
engineered on multiple control levels.
\textbf{QUELLE}
(except some end-to-end learning control methods).
While on a lower control level,
an onboard autopilot is 
permanently maintaining attitude and altitude of the UAV
in order to prevent 
collisions and keep up maneuverability,
on a higher level, different actors 
can navigate the drone and perform maneuvers.
Either a human pilot steers the UAV remotely from
the GCS per radio transmitter (RC)
thereby, relying on direct visual contact to the vehicle 
or on video stream from an onboard camera,
or an onboard computer constantly executes 
algorithms to track trajectories
thereby, relying on sensor data.
While traditional navigation approaches,
such as VIO or SLAM
evaluate sensor data received from
GPS, radio, inertial, SLAM, VIO
to estimate the pose of the UAV,
new approaches basing
on camera or LIDAR data utilize perception concepts
of machine learning.
These computer tracked trajectories 
are either static,
as part of a
precomputed mission or 
adaptive to dynamic environments
in sense of autonomous flight.


\subsection{Autonomous Flight}

Ability to avoid obstacles
static and dynamic???





\subsection{Autonomy}
The concept of autonomy extends
automation 
onto unexpected situations. 
Automation replaces human action
to complete well known tasks in well known, structured environments.
While an automated system outperforms humans
with respect to 
precision, speed and costs,
it is unable to
cope with unexpected situations
since it is engineered to rely on limited
parameters, variations and disturbances.
In addition to an automated system,
an autonomous system, 
due to a deeper based perception,
is capable of anticapating upcoming events,
making decisions and reacting properly - like humans.
It can perform previously unknown tasks
in previously unknown, dynamically changing environments,
deal with uncertainty and learn from its failures.
The design of an autonomous system
requires the composition of
various methods from 
control theory,
system identification, 
system estimation,
communication theory,
computer science (in particular artificial intelligence)
and
operations research.
Furthermore, with machines making decisions,
questions of other fields concerning
ethics,
responsibility,
legality
arise.


\subsection{Hierarchical Control Architecture of a Fully Autonomous UAV}

In contrast to RPV...

Involving the concept of 
increasing precision with decreasing intelligence (IPDI),
control architectures of autonomous systems for UAVs 
can be functionally layered
into three control levels, i.e.
organization, coordination, and execution
as well as a supervisor level
to enable human intervention.

Downstream, from higher to lower levels,
commands are distributed and
system parameters are modified.

Upstream, from lower to higher level,
command responses and sensor data
%e.g. status, health information, 
are passed.

Information may also be exchanged within the same level.

The higher the control level,
the longer the interval of planning and execution time.



All three levels have access to
information about 
environment and state estimates of the UAV.

The least intelligent \textbf{execution level}
interfaces with sensors and actuators
of the UAV. While receiving sensor data about
the state of the UAV and the environment,
this level runs conventional  control  algorithms 
on inner-loop and sends low level control
commands directly to the actuators of the UAV.



(These algortightms very good researched)




It  senses  the  responses  of  the  vehicle  and  environment,    
processes    them    to    identify    parameters,    
estimates   states,   or   detects   failures,   
and   passes   this   information to the higher levels.


\paragraph{Organization Level}

highest   intelligent    and    lowest    precision
involves    intelligent,    decision-making  methods,  
situation  evaluation  and  mission  management. 




\paragraph{Coordination Level}

The  middle  level
interface between the actions of the other  two  levels  
combination  of  conventional  and   intelligent   decision   making   methods.   
outer-loop

middle-loop  to  generate  the  trajectory,  guidance  and  other  signals




%https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5375937


\subsection{Autonomous Navigation Systems for Small Quadcopters}
Flight Control Pipeline


\paragraph{Classical System Architecture}
Env - Sensor - State (Velocity) Estimation                              - Velocity Controller - Flight Controller - Motors
             - obstacle detection - local planner - position controller -


\paragraph{Camera Based System Architecture For Reactive Flight Control Pipeline}

\paragraph{System Architecture For Fully End-to-End LIDAR Based Reactive Flight Control
Pipeline}


\paragraph{LIDAR to Actions System Architecture}

QUELLE SAMZENG

In case of a small UAV,
one major point is to
guarantee that the algorithms
can be executed in real time
since onboard hardware is constrained
by small payloads.



\paragraph{Challenges}





<
There  has  been  many  significant  research  in  making  UAV  fly  autonomously,  but  obstacle  avoidance  is  still  a  crucial   hurdle.   For   small   quadrotor   UAV,   due   to   the   limitation  of  payloads  it  is  infeasible  to  carry  sophisticated  radar  sensors.  Though  many  advanced  research  has  used  light  detection  and  ranging(LiDAR)  [1]  or  the  cameras  of  Microsoft Kinect [2], both sensors are heavy, which will lead to  increase  the  power  consumption  and  drastically  decrease  the flight time.
>
SOURCE 

<
Autonomous flight is in contrast to other
control methods, i.e. radio remote and preprogrammed.
    communication  link  is  not  expedited  or  reliable
    doesn’t  update  mission  when  plans  or  treat  situations  are  changed
    rapidly  changing  uncertain  environment the present techniques are inadequat

perform  well  under  significant  uncertainties  inthe  system  and  environment for extended periods of time
compensate  for  system  failures  without  external  intervention

techniques  from  the  field  of  Artificial  Intelligence  (AI)  
    evolve  from  conventional  control  systems  by  adding  intelligent  components,  and  their  development requires interdisciplinary research [3]. 

Autonomous  controllers  have  the  power  and  ability  for  self  governance  in  the  performance  of  control  functions.
high  degree   of   automation   is   applied   in   a   very   unstructured   environment
“Automation”  here  refers  to  the  absence  of  human   intervention,
“unstructured   environment”   is   associated with uncertainty

integrates concepts and methods from areas such as Control, Identification,   Estimation,   and   Communication   Theory,   Computer   Science,   especially   Artificial   Intelligence,   and   Operations  Research  (OR).  
The   synthesis   of   high   performance   controllers  for  the  solution  of  difficult  control  problems  is  what autonomous control is really all about.  

>
%https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5375937

%-----------------------------------
%	SUBSECTION 1
%-----------------------------------
\subsection{Traditional Approaches}

HERE

%-----------------------------------
%	SUBSECTION 2
%-----------------------------------

\subsection{Newly Developed}
HERE


Due to the inherent instability of the system, constant control commands must be applied to
prevent a collision. In the event the robot enters an environment where \textbf{accurate state estimation}
is computationally impossible due to lack of features, we still want the system to do its best given
available information to prevent immediate collision.













%----------------------------------------------------------------------------------------
%	SECTION 5
%----------------------------------------------------------------------------------------

\section{Research on Drone Racing}

