% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Chapter1} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Creative Introduction}

Search and find, order and pay, evaluate and reclame - 
alltogether, nowadays, only one click away.
The final step, however, deliver the parcel to 
the customer remains a process that lasts for days.
While digital revolution has been providing
extensive flexibility due to an
information exchange at the speed of light,
traditionally grown structures operating in real world
have not been able to follow such an acceleration
and will never be due to physical constraints.
Nevertheless,
great advancements in parcel shipping are in sight.
From globally operating companies down to start ups as well as
universities and research centers are 
doing research on solutions to 
parcel delivery by unmanned aerial vehicles (UAV)
in order to drastically reduce delivery time and costs.
Besides, due to vast, further research,
many other areas of applications for UAV technology
has been arising, e.g. aerial surveillance, monitoring of existing architectures.
Due to strong benefits of UAV technology,
e.g. cost efficiency, process optimization, sustainability,
independence of infrastructure, etc.,
UAV technology likely will establish in daily life
and industry.
However,
UAV technology has yet gone into action only sporadically
waiting for its breakthrough.

The breakthrough is closely coupled with
achieving high robustness of autonomous flight.
Guaranteeing safety at high speeds and high flight performance,
is crucial to
responsibely and economically apply autonomous UAV technology
exspecially in areas with human civilization.

\cite{loquercio2018learning}.